---
title: "XYZ_co PG"
output: 
  html_document: 
    fig_width: 12
    fig_height: 12
    toc_depth: 4
date: "2023-03-28"
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(TSstudio)
library(forecast)
library(tseries)
library(imputeTS)
library(lmtest) # for coeftest
library(dplyr) #unload to ensure stats::lag() is used instead and slightly shorten extensive var names in model fitting
library(lubridate)
library(lmtest) # for coeftest()

```


<!-- Set up and Data Cleaning -->
```{r}
#Initialize and arrange by date
XYZ_co_Data_03_15_2023_LW$date[1] <- "1899-12-01"
XYZ_co_Data_03_15_2023_LW$date <- as.Date(XYZ_co_Data_03_15_2023_LW$date)
XYZ_co_Data_03_15_2023_LW <- XYZ_co_Data_03_15_2023_LW %>%  arrange(date)
```

```{r}
#Change Recession info into a Dummy variable, 1 if recession, 0 if not.
  
isRecession <-NULL
for (i in 1:length(XYZ_co_Data_03_15_2023_LW$recession)) {
  if (is.na(XYZ_co_Data_03_15_2023_LW$recession[i])) {
    isRecession[i] <- 0
  }
    else {
      isRecession[i] <- 1
  }
}
#Create Indicator Variables instead. Redundancy
covidRec <- isRecession
covidRec[c(1:1441, 1445:1477)] <- 0
greatRec <- rep(0, each = 1477)
greatRec[1296:1314] <- 1
early2000Rec <- rep(0,each = 1477)
early2000Rec[1215:1223] <- 1

#Create Interaction variables as needed to check with Prewhitening or include in model fitting
GDPYoYxUnempClaimsAdj <- XYZ_co_Data_03_15_2023_LW$GDP_YoY * log(XYZ_co_Data_03_15_2023_LW$Unemployment_Claims_Adj)
CPIAdjSq <- XYZ_co_Data_03_15_2023_LW$CPI_Adj ^2
UnempXSavings <- XYZ_co_Data_03_15_2023_LW$Unemployment_Rate_Adj * XYZ_co_Data_03_15_2023_LW$Savings_Rate

#Create Month Indicator Variables
allMonths <- month((XYZ_co_Data_03_15_2023_LW$date))
novInd <- ifelse(allMonths==11, 1, 0)
decInd <- ifelse(allMonths==12, 1, 0)
janInd <- ifelse(allMonths==1, 1, 0)
febInd <- ifelse(allMonths ==2, 1,0)


# CPIAdjxDebt <- XYZ_co_Data_03_15_2023_LW$CPI_Adj * XYZ_co_Data_03_15_2023_LW$Debt
# CPIxDebt <- XYZ_co_Data_03_15_2023_LW$CPI * XYZ_co_Data_03_15_2023_LW$Debt
XYZ_co_dat <- cbind(XYZ_co_Data_03_15_2023_LW, early2000Rec, greatRec, covidRec, CPIAdjSq, UnempXSavings, novInd, decInd, janInd, febInd)
# head(XYZ_co_dat)

```

```{r}
#Master TS, interpolate missing XYZ_co revenue
myTS <- XYZ_co_dat[1288:1475,c(4:31,33,34,37:48)] %>% ts(start = c(2007,3), end = c(2022,10), freq = 12) %>%na_kalman()


#Removal of Hourly earning to increase date range by 50%
myTS2 <- XYZ_co_dat[1190:1475, c(4:12,17:31,33,34,37:48)] %>% ts(start = c(1999,1), end = c(2022,10), freq = 12) %>% na_kalman()



```


```{r}
#Impute previously converted NA values 
# myTsAnomFree <- na_interpolation(myTsAnomFree)
# ts_plot(myTsAnomFree)
```

Prewhitening used to identify possible terms for lagged regression. (https://online.stat.psu.edu/stat510/lesson/9/9.1)
<!-- Prewhitening Attempt 1: Manually  -->
```{r}
# Sort IVs into lists of approx. likely AR and differencing orders
for (i in c(1:24, 29:36)) {
  ccf(myTS2[,i],myTS2[,31], main = colnames(myTS2)[i], lag.max = 24)
  acf(myTS[,i], main = colnames(myTS)[i])
  pacf(myTS[,i], main = colnames(myTS)[i])
}
```

```{r}
#Determined using last chunks acf/pacf.
seasList <- c(3,  20, 23, 25)
diffList <- c(1,2, 4, 6, 7, 10, 11, 12, 13, 14, 15, 18, 19, 21, 22, 24, 26, 27, 28, 34)
diffnSeasList <- c(11, 12, 13, 15, 19, 22, 27)
ar1list <- c(25)
ar2list <- c(3,5, 16, 17, 20, 23)
ar3list<- c(8, 9)
```

```{r}
#Determine best AR order for IVs that need differencing
for (i in diffList) {
  ccf(diff(myTS[,i], differences = 1),myTS[,31], main = i, lag.max = 48)
  acf(diff(myTS[,i], differences = 1), main = colnames(myTS)[i])
  pacf(diff(myTS[,i], differences = 1), main = colnames(myTS)[i])
}
```

```{r}
#Sorted with last chunk
diffar1List <- c(14, 19 )
diffar2List <- c(2, 4, 10, 11, 12, 13,15, 21,24, 28)
diffar3List <- c(18, 22)
noList <- c(1, 6, 7, 26, 27)
y_i <- 31
```

General Idea of Prewhitening: plot a CCF  of filtered y values against x residuals found in approx AR and I orders.
Y values are filtered by the x coefficients in approx ARI model. This process is highly discretionary.
```{r}
#Prewhitening y based on AR 1 IVs
for (i in ar1list) {
  tempMd <- NULL
  pwTemp <- NULL
  pwXYZ_coTemp <- NULL
  tempC <- NULL
  #Apply approx ARI order
  tempMd <- arima(myTS[,i], order = c(1,0,0))
  tempC <- tempMd$coef
  pwTemp <-tempMd$residuals
  #Filtered y Values
  pwXYZ_coTemp <- stats::filter(myTS[,y_i], method = "recursive", filter = c(-tempMd$coef, 1), side = 1)
  ccf(pwTemp, pwXYZ_coTemp, na.action = na.omit, main = colnames(myTS)[i])
}
```
Repeat for other lists
```{r}
#Prewhitening based on AR2 IVs
for (i in ar2list) {
  tempMd <- NULL
  pwTemp <- NULL
  pwXYZ_coTemp <- NULL
  tempMd <- arima(myTS[,i], order = c(2,0,0))
  print(tempMd$coef)
  pwTemp <-tempMd$residuals
  pwXYZ_coTemp <- stats::filter(myTS[,y_i], filter = c(1, -tempMd$coef[1], -tempMd$coef[2], tempMd$coef[1]*tempMd$coef[2]), side = 1)
  ccf(pwTemp, pwXYZ_coTemp, na.action = na.omit, main = colnames(myTS)[i])
}
```

```{r}
#Prewhitening based on AR3 IVs
for (i in ar3list) {
  tempMd <- NULL
  pwTemp <- NULL
  pwXYZ_coTemp <- NULL
  tempC <- NULL
  tempMd <- arima(myTS[,i], order = c(3,0,0))
  pwTemp <-tempMd$residuals
  tempC <- tempMd$coef
  # print(tempC)
  pwXYZ_coTemp <- stats::filter(myTS[,y_i], filter = c(1, -tempC[1], -tempC[2], tempC[1]*tempC[2]-tempC[3], tempC[1]*tempC[3], tempC[2]*tempC[3], -tempC[1]*tempC[2]*tempC[3]), side = 1)
  ccf(pwTemp, pwXYZ_coTemp, na.action = na.omit, main = colnames(myTS)[i])
}
```

```{r}
#Prewhitening based on differenced AR 1 IVs
for (i in diffar1List) {
  tempMd <- NULL
  pwTemp <- NULL
  pwXYZ_coTemp <- NULL
  tempC <- NULL
  tempMd <- arima(myTS[,i], order = c(1,1,0))
  pwTemp <-tempMd$residuals
  tempC <- tempMd$coef
  print(tempC)
  pwXYZ_coTemp <- stats::filter(myTS[,y_i], filter = c(1, -1-tempC[1], -tempC[1]), side = 1)
  ccf(pwTemp, pwXYZ_coTemp, na.action = na.omit, main = colnames(myTS)[i], lag.max = 48)
}
```

```{r}
#Prewhitening based on differenced AR 2 IVs
for (i in diffar2List) {
  tempMd <- NULL
  pwTemp <- NULL
  pwXYZ_coTemp <- NULL
  tempC <- NULL
  tempMd <- arima(myTS[,i], order = c(2,1,0))
  pwTemp <-tempMd$residuals
  tempC <- tempMd$coef
  print(tempC)
  pwXYZ_coTemp <- stats::filter(myTS[,y_i], filter = c(1, -1-tempC[1], -tempC[1]-tempC[2], tempC[2]+tempC[1]*tempC[2], tempC[1]*tempC[2]), side = 1)
  ccf(pwTemp, pwXYZ_coTemp, na.action = na.omit, main = colnames(myTS)[i])
}
```

```{r}
#Prewhitening based on differenced AR 3 IVs
for (i in diffar3List) {
  tempMd <- NULL
  pwTemp <- NULL
  pwXYZ_coTemp <- NULL
  tempC <- NULL
  tempMd <- arima(myTS[,i], order = c(3,1,0))
  pwTemp <-tempMd$residuals
  tempC <- tempMd$coef
  print(tempC)
  pwXYZ_coTemp <- stats::filter(myTS[,y_i], filter=c(1, -tempC[1]-1, -tempC[2]+tempC[1], tempC[1]*tempC[2]-tempC[3]+tempC[2], tempC[1]*tempC[3] - (tempC[1]*tempC[2] -tempC[3]), tempC[2]*tempC[3]-tempC[1]*tempC[3], -tempC[1]*tempC[2]*tempC[3] - tempC[2]*tempC[3], tempC[1]*tempC[2]*tempC[3]), side = 1)
  ccf(pwTemp, pwXYZ_coTemp, na.action = na.omit, main = colnames(myTS)[i])
}
```

More approaches used as the prior method didn't use MA orders for simplicity, and had high complexity determining the filter function.

<!-- Prewhitening Approach 2: Using TSA::prewhiten(). Limited to AR models only. Automatic and may not be correct -->

```{r}
library(TSA)
for(i in c(1:24, 29:36)){
  prewhiten(myTS2[,i], myTS2[,27],lag.max = 24,  main = colnames(myTS2)[i])
}
```


<!-- Prewhitening Approach 3: Using TSA::prewhiten() again, but with auto.arima on IVs to possibly capture MA and seasonality. Cautions: automatic and possibly not correct. Doesn't show which orders used -->

```{r}
#Caution: Lengthy Processing time expected, possibly 30 minutes.
for(i in c(1:28, 35:39)){
  tempArima <- auto.arima(myTS[,i], stepwise = FALSE, approximation = FALSE)
  whiteY <- residuals(Arima(myTS[,31], model = tempArima))
  ccf(myTS[,i], whiteY, main = colnames(myTS)[i], lag.max = 24 )
}
```





<!-- Observations while compiling lags/leads. Generally determined by which side had stronger/more spikes. -->

More likely to be Lagging:
Unemp Rate Adj, Unemp Claims, Hourly Earnings YoY, Debt, Home Sales Adj, Recessions

More likely to be leading:
S&P, GDP Unemp Rate, Hourly Earnings, CPI, Available Credit, Disp Income, Saving Rate, New Home Sales Adj



```{r}
#Significant lags from Prewhitening
y <- log(myTS[,31])
xLag <- cbind(
  lag(myTS[,"S&P500"], -2),
  lag(myTS[,"GDP"], -20),
  lag(myTS[,"GDP_YoY"], -1),
  lag(myTS[,"PCE"], -20),
  lag(myTS[,"Unemployment_Rate"], -8),
  lag(myTS[,"Unemployment_Rate"], -20),
  lag(myTS[,"Unemployment_Rate_Adj"], -3),
  lag(myTS[,"Unemployment_Rate_Adj"], -11),
  myTS[,"Unemployment_Claims"],
  lag(myTS[,"Unemployment_Claims"], -10),
  lag(myTS[,"Unemployment_Claims"], -13),
  myTS[,"Hourly_Earnings_Adj"],
  lag(myTS[,"Hourly_Earnings_Adj"], -6),
  lag(myTS[,"CPI_Adj"], -12),
  lag(myTS[,"CPI_Adj"], -15),
  lag(myTS[,"Available_Credit"], -20),
  lag(myTS[,"CCI"], -2),
  lag(myTS[,"Debt"], -1),
  lag(myTS[,"Debt"], -6),
  lag(myTS[,"Debt"], -10),
  lag(myTS[,"Debt"], -11),
  lag(myTS[,"Savings_Rate"], -8),
  lag(myTS[,"Savings_Rate"], -19),
  lag(myTS[,"Home_Sales_Adj"], -1),
  lag(myTS[,"Home_Sales_Adj"], -8),
  myTS[,"Plans_to_Buy_Automobile"]
) 
```

<!-- Significant leads found in prior prewhitening CCFs(not exhaustive) -->

Leads:S&P 8, 10
GDP: 4, 10. Yoy 12
PCE: 5, 14, 18
Unemp Rate: 2, 5
Adj: 13
Unemp Claims: 1, 13,14
Hourly: 5. Adj 6
CPI: 6. Adj: 3, 15
Avail Cred: 12, 13, 17
Disp Income: 11, 1to 24 YoY 11 + 16, 23
Savings: 4, 11
Homes Adj: 1, 14, 7, 15
New Homes Adj: 10,11,12, 13
GDPxUnemp: 1,2,13, 21,2,13

Note: Stepwise regression was used in statistical software JMP to help expand the list of possible lags/leads, possible interactions.

<!-- Model Fitting General Idea: Create a large list of possible variables with lags/leads. Utilize arima() with xreg("x regressors" or IVs) argument. Add as many variables to xreg as possible with no (Seasonal) ARIMA orders to capture as much of the series with regressors, then tweak the order and included regressors until residual assumptions are met in checkresiduals(). -->



# ```{r}
# #Attempt with stepwise found sig lags, create lags of var
# stepLags <- cbind(
#   myTS2[,27],
#   lag(myTS2[,"Home_Sales_Adj"], -8),
#   lag(myTS2[,"Home_Sales_Adj"], -9),
#   lag(myTS2[,"Home_Sales_Adj"], -10),
#   lag(myTS2[,"Savings_Rate"], -8),
#   lag(myTS2[,"Savings_Rate"], -19),
#   lag(myTS2[,"Debt"], -6),
#   lag(myTS2[,"Debt"], -9),
#   log(lag(myTS2[,"Disposable_Income"], -13)),
#   log(lag(myTS2[,"Disposable_Income"], -24)),
#   # lag(myTS2[,"Available_Credit"], -1),
#   lag(myTS2[,"Available_Credit"], -24),
#   lag(myTS2[,"CPI_Adj"], -9),
#   lag(myTS2[,"CPI_Adj"], -12),
#   lag(myTS2[,"CPI_Adj"], -14),
#   lag(myTS2[,"CPI_Adj"], -17),
#   # lag(myTS2[,"CPI_Adj"], -24),
#   lag(myTS2[,"Unemployment_Rate"], -8),
#   lag(myTS2[,"Unemployment_Rate"], -20),
#   lag(myTS2[,"Unemployment_Claims"], -10),
#   lag(myTS2[,"Unemployment_Claims"], -20),
#   lag(myTS2[,"S&P500"], -1),
#   lag(myTS2[,"S&P500"], -9),
#   lag(myTS2[,"GDP_YoY"], -1),
#   # lag(myTS2[,"GDP_YoY"], -20),
#   # lag(myTS2[,"PCE_YoY"], -8),
#   # lag(myTS2[,"PCE_YoY"], -20),
#   # lag(myTS2[,"isRecession"], -1),
#   lag(myTS2[,"isRecession"], -10),
#   lag(myTS2[,"isRecession"], -12),
#   # lag(myTS2[,"isRecession"], -22),
#   lag(myTS2[,"isRecession"], -23)
# )
#   
# ```

```{r}
#Attempt 2 with PW lags
stepLags2 <- cbind(
  myTS2[,27],
  # lag(myTS2[,"Home_Sales_Adj"], -5),
  # lag(myTS2[,"Home_Sales_Adj"], -9),
  # lag(myTS2[,"Home_Sales_Adj"], -10),
  # lag(myTS2[,"Home_Sales_Adj"], -11),
  lag(myTS2[,"Home_Sales_Adj"], -17),
  # lag(myTS2[,"Home_Sales_Adj"], -20),
  # lag(myTS2[,"New_Home_Sales_Adj"], -4),
  lag(myTS2[,"New_Home_Sales_Adj"], -7),
  # lag(myTS2[,"New_Home_Sales_Adj"], -9),
  # lag(myTS2[,"New_Home_Sales_Adj"], -11),
  # lag(myTS2[,"New_Home_Sales_Adj"], -14),
  # lag(myTS2[,"New_Home_Sales_Adj"], -16),
  # lag(myTS2[,"New_Home_Sales_Adj"], -18),
  # lag(myTS2[,"New_Home_Sales_Adj"], -20),
  # lag(myTS2[,"New_Home_Sales_Adj"], -21),
  # log(lag(myTS2[,"Savings_Rate"], -7)),
  # log(lag(myTS2[,"Savings_Rate"], -8)),
  # log(lag(myTS2[,"Savings_Rate"], -16)),
  # log(lag(myTS2[,"Savings_Rate"], -19)),
  # lag(myTS2[,"Debt"], -10),
  # lag(myTS2[,"Debt"], -11),
  # lag(myTS2[,"Debt"], -13),
  # lag(myTS2[,"Debt"], -14),
  # lag(myTS2[,"Debt"], -16),
  # lag(myTS2[,"Debt"], -17),
  # lag(myTS2[,"Debt"], -23),
  # lag(myTS2[,"CCI"], -10),
  # lag(myTS2[,"CCI"], -14),
  # lag(myTS2[,"CPI_Adj"], -9),
  # lag(myTS2[,"CPI_Adj"], -14),
  # lag(myTS2[,"CPI_Adj"], -17),
  # log(lag(myTS2[,"Available_Credit"], -19)),
  # log(lag(myTS2[,"Disposable_Income"], -13)),
  # log(lag(myTS2[,"Disposable_Income"], -11)),
  # log(lag(myTS2[,"Disposable_Income_YoY"], -8)),
  # log(lag(myTS2[,"Disposable_Income_YoY"], -9)),
  # log(lag(myTS2[,"Unemployment_Rate_Adj"], -5)),
  # log(lag(myTS2[,"Unemployment_Rate_Adj"], -13)),
  # log(lag(myTS2[,"Unemployment_Rate_Adj"], -11)),
  # log(lag(myTS2[,"Unemployment_Rate_Adj"], -17)),
  # log(lag(myTS2[,"Unemployment_Claims_Adj"], -7)),
  # log(lag(myTS2[,"Unemployment_Claims_Adj"], -8)),
  # log(lag(myTS2[,"Unemployment_Claims_Adj"], -10)),
  log(lag(myTS2[,"Unemployment_Claims_Adj"], -11)),
  # log(lag(myTS2[,"Unemployment_Claims_Adj"], -22)),
  # log(lag(myTS2[,"Unemployment_Claims_Adj"], -23)),
  # lag(myTS2[,"GDP_YoY"], -1),
  # lag(myTS2[,"GDP_YoY"], -3),
  # lag(myTS2[,"GDP_YoY"], -19),
  # lag(myTS2[,"PCE_YoY"], -18),
  lag(myTS2[,"PCE_YoY"], -19),
  # lag(myTS2[,"PCE"], -20),
  # lag(myTS2[,"GDP"], -10),
  # myTS2[,"covidRec"],
  # lag(myTS2[,"covidRec"], -2),
  # lag(myTS2[,"greatRec"], -2),
  # lag(myTS2[,"greatRec"], -6),
  # lag(myTS2[,"greatRec"], -7),
  # myTS2[,"early2000Rec"],
  # lag(myTS2[,"isRecession"], -10),
  # lag(myTS2[,"isRecession"], -22),
  # lag(myTS2[,"isRecession"], -23),
  # lag(myTS2[,"Plans_to_Buy_Automobile"], -3),
  # lag(myTS2[,"Plans_to_Buy_Automobile"], -10),
  # lag(myTS2[,"Plans_to_Buy_Automobile"], -14),
  # lag(myTS2[,"Plans_to_Buy_Automobile"], -19),
  # lag(myTS2[,"Plans_to_Buy_Automobile"], -21),
  # log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -3)),
  # log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -7)),
  # log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -10)),
  # log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -11)),
  # log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -12)),
  log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -13)),
  # log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -15)),
  # log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -23)),
  # lag(myTS2[,"CPIxDebt"], -20)
  # lag(myTS2[,"CPIAdjxDebt"], -8),
  # lag(myTS2[,"CPIAdjxDebt"], -10),
  # lag(myTS2[,"CPIAdjxDebt"], -13),
  lag(myTS2[,"CPIAdjxDebt"], -14)
  # lag(myTS2[,"CPIAdjxDebt"], -20)
)
#Fit a model with stepwise found lags
#(1,0,2)(1,0,1)
  fitStep <- arima(stepLags2[25:285,1], order = c(1,0,0), seasonal = list(order = c(1,0,0), period = 12), xreg = stepLags2[25:285,-1], include.mean = FALSE, method = "ML")
# fitStep <- auto.arima(stepLags2[25:285,1], xreg = stepLags2[25:285,-1], approximation = FALSE, stepwise = FALSE)
# summary(fitStep)
# pacf(fitStep$residuals, lag.max = 48)
checkresiduals(fitStep)
coeftest(fitStep)

```

```{r}
#Attempt 3 with limit data 170:285
stepLags3 <- cbind(
  myTS2[,27],
  # lag(myTS2[,"Home_Sales_Adj"], -5),
  # lag(myTS2[,"Home_Sales_Adj"], -9),
  # lag(myTS2[,"Home_Sales_Adj"], -10),
  # lag(myTS2[,"Home_Sales_Adj"], -11),
  lag(myTS2[,"Home_Sales_Adj"], -17),
  # lag(myTS2[,"Home_Sales_Adj"], -20),
  # lag(myTS2[,"New_Home_Sales_Adj"], -4),
  lag(myTS2[,"New_Home_Sales_Adj"], -7),
  # lag(myTS2[,"New_Home_Sales_Adj"], -9),
  # lag(myTS2[,"New_Home_Sales_Adj"], -11),
  # lag(myTS2[,"New_Home_Sales_Adj"], -14),
  # lag(myTS2[,"New_Home_Sales_Adj"], -16),
  # lag(myTS2[,"New_Home_Sales_Adj"], -18),
  # lag(myTS2[,"New_Home_Sales_Adj"], -20),
  # lag(myTS2[,"New_Home_Sales_Adj"], -21),
  # log(lag(myTS2[,"Savings_Rate"], -7)),
  # log(lag(myTS2[,"Savings_Rate"], -8)),
  # log(lag(myTS2[,"Savings_Rate"], -16)),
  # log(lag(myTS2[,"Savings_Rate"], -19)),
  # lag(myTS2[,"Debt"], -10),
  # lag(myTS2[,"Debt"], -11),
  # lag(myTS2[,"Debt"], -13),
  # lag(myTS2[,"Debt"], -14),
  # lag(myTS2[,"Debt"], -16),
  # lag(myTS2[,"Debt"], -17),
  # lag(myTS2[,"Debt"], -23),
  # lag(myTS2[,"CCI"], -10),
  # lag(myTS2[,"CCI"], -14),
  # lag(myTS2[,"CPI_Adj"], -9),
  # lag(myTS2[,"CPI_Adj"], -14),
  # lag(myTS2[,"CPI_Adj"], -17),
  # log(lag(myTS2[,"Available_Credit"], -19)),
  # log(lag(myTS2[,"Disposable_Income"], -13)),
  # log(lag(myTS2[,"Disposable_Income"], -11)),
  # log(lag(myTS2[,"Disposable_Income_YoY"], -8)),
  # log(lag(myTS2[,"Disposable_Income_YoY"], -9)),
  # log(lag(myTS2[,"Unemployment_Rate_Adj"], -5)),
  # log(lag(myTS2[,"Unemployment_Rate_Adj"], -13)),
  # log(lag(myTS2[,"Unemployment_Rate_Adj"], -11)),
  # log(lag(myTS2[,"Unemployment_Rate_Adj"], -17)),
  # log(lag(myTS2[,"Unemployment_Claims_Adj"], -7)),
  # log(lag(myTS2[,"Unemployment_Claims_Adj"], -8)),
  # log(lag(myTS2[,"Unemployment_Claims_Adj"], -10)),
  log(lag(myTS2[,"Unemployment_Claims_Adj"], -11)),
  # log(lag(myTS2[,"Unemployment_Claims_Adj"], -22)),
  # log(lag(myTS2[,"Unemployment_Claims_Adj"], -23)),
  # lag(myTS2[,"GDP_YoY"], -1),
  # lag(myTS2[,"GDP_YoY"], -3),
  # lag(myTS2[,"GDP_YoY"], -19),
  # lag(myTS2[,"PCE_YoY"], -18),
  lag(myTS2[,"PCE_YoY"], -19),
  # lag(myTS2[,"PCE"], -20),
  # lag(myTS2[,"GDP"], -10),
  # myTS2[,"covidRec"],
  # lag(myTS2[,"covidRec"], -2),
  # lag(myTS2[,"greatRec"], -2),
  # lag(myTS2[,"greatRec"], -6),
  # lag(myTS2[,"greatRec"], -7),
  # myTS2[,"early2000Rec"],
  # lag(myTS2[,"isRecession"], -10),
  # lag(myTS2[,"isRecession"], -22),
  # lag(myTS2[,"isRecession"], -23),
  # lag(myTS2[,"Plans_to_Buy_Automobile"], -3),
  # lag(myTS2[,"Plans_to_Buy_Automobile"], -10),
  # lag(myTS2[,"Plans_to_Buy_Automobile"], -14),
  # lag(myTS2[,"Plans_to_Buy_Automobile"], -19),
  # lag(myTS2[,"Plans_to_Buy_Automobile"], -21),
  # log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -3)),
  # log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -7)),
  # log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -10)),
  # log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -11)),
  # log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -12)),
  log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -13)),
  # log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -15)),
  # log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -23)),
  # lag(myTS2[,"CPIxDebt"], -20)
  # lag(myTS2[,"CPIAdjxDebt"], -8),
  # lag(myTS2[,"CPIAdjxDebt"], -10),
  # lag(myTS2[,"CPIAdjxDebt"], -13),
  lag(myTS2[,"CPIAdjxDebt"], -14)
  # lag(myTS2[,"CPIAdjxDebt"], -20)
)
#Fit a model with stepwise found lags
#(1,0,2)(1,0,1)
  fitLim <- arima(stepLags3[170:285,1], order = c(1,0,2), seasonal = list(order = c(1,0,1), period = 12), xreg = stepLags3[170:285,-1], include.mean = FALSE, method = "ML")
# fitStep <- auto.arima(stepLags2[25:285,1], xreg = stepLags2[25:285,-1], approximation = FALSE, stepwise = FALSE)
# summary(fitStep)
# pacf(fitStep$residuals, lag.max = 48)
checkresiduals(fitLim)
coeftest(fitLim)

```



```{r}

```
Lags from Stepwise:
Homes Sales Adj:  10, 11, 12, 20
New Home Sales Adj: 9, 11, 16, 21, 24
Savings Rate: 7, 19
Debt: 10, 13, 17, 23, 24
Disposable Income: 13, 24
Available Credit: 1, 24
CPI ADJ: 9, 12, 14, 17, 24, CPI: 12, 15
Unemp Rate: 7, ADJ: 6
Claims: 8, 20, ADJ: 8, 20
S&P: 1, 9
GDP: 7, 24, YOY: 8, 20
PCE: 7, 24, YOY: 8, 20
COVID: 10, 22
Early 2000s: 12, 23
Great rec: 1, 22

Interaction:
GDPYoY * Unemp Claims Adj: -13
CPI * Debt: -8, -20




```{r}
# #Fit a model with stepwise found lags
# fitStep <- arima(stepLags[25:286,1], order = c(1,0,2), seasonal = list(order = c(0,1,1), period = 12), xreg = stepLags[25:286,-1])
# # fitStep <- auto.arima(stepLags[25:286,1], xreg = stepLags[25:286,-1], approximation = FALSE, stepwise = FALSE)
# summary(fitStep)
# checkresiduals(fitStep)
# pacf(fitStep$residuals)
```
1,0,2,0,1,1,12
Unemp rate adj -13
gdp yoy -1 .08
<!-- ```{r} -->
coeftest(fitStep)


```{r}
for(i in c(2:length(wleadsAll[1,]))){
  plot(wleadsAll[25:285,i],fitStep$residuals,  main = colnames(wleadsAll)[i])
}
```


```{r}
# for(i in c(2:length(allStepLags2[1,]))){
#   ts.plot((allStepLags2[25:285,i]/sqrt(sum(allStepLags2[25:285,i]))),fitStep$residuals,  main = colnames(allStepLags2)[i])
# }

```

```{r}
#Attempt 2 with PW lags
allStepLags2 <- cbind(
  myTS2[,27],
  lag(myTS2[,"Home_Sales_Adj"], -5),
  lag(myTS2[,"Home_Sales_Adj"], -9),
  lag(myTS2[,"Home_Sales_Adj"], -10),
  lag(myTS2[,"Home_Sales_Adj"], -11),
  lag(myTS2[,"Home_Sales_Adj"], -17),
  lag(myTS2[,"Home_Sales_Adj"], -20),
  lag(myTS2[,"New_Home_Sales_Adj"], -4),
  lag(myTS2[,"New_Home_Sales_Adj"], -7),
  lag(myTS2[,"New_Home_Sales_Adj"], -9),
  lag(myTS2[,"New_Home_Sales_Adj"], -11),
  lag(myTS2[,"New_Home_Sales_Adj"], -16),
  lag(myTS2[,"New_Home_Sales_Adj"], -18),
  lag(myTS2[,"New_Home_Sales_Adj"], -20),
  lag(myTS2[,"New_Home_Sales_Adj"], -21),
  log(lag(myTS2[,"Savings_Rate"], -7)),
  log(lag(myTS2[,"Savings_Rate"], -8)),
  log(lag(myTS2[,"Savings_Rate"], -16)),
  log(lag(myTS2[,"Savings_Rate"], -19)),
  lag(myTS2[,"Debt"], -10),
  lag(myTS2[,"Debt"], -11),
  lag(myTS2[,"Debt"], -13),
  lag(myTS2[,"Debt"], -14),
  lag(myTS2[,"Debt"], -16),
  lag(myTS2[,"Debt"], -17),
  lag(myTS2[,"Debt"], -23),
  lag(myTS2[,"CCI"], -10),
  lag(myTS2[,"CCI"], -14),
  lag(myTS2[,"CPI_Adj"], -9),
  lag(myTS2[,"CPI_Adj"], -14),
  lag(myTS2[,"CPI_Adj"], -17),
  log(lag(myTS2[,"Available_Credit"], -19)),
  log(lag(myTS2[,"Disposable_Income"], -13)),
  log(lag(myTS2[,"Disposable_Income"], -11)),
  log(lag(myTS2[,"Disposable_Income_YoY"], -8)),
  log(lag(myTS2[,"Disposable_Income_YoY"], -9)),
  log(lag(myTS2[,"Unemployment_Rate_Adj"], -5)),
  log(lag(myTS2[,"Unemployment_Rate_Adj"], -13)),
  log(lag(myTS2[,"Unemployment_Rate_Adj"], -11)),
  log(lag(myTS2[,"Unemployment_Rate_Adj"], -17)),
  log(lag(myTS2[,"Unemployment_Claims_Adj"], -7)),
  log(lag(myTS2[,"Unemployment_Claims_Adj"], -8)),
  log(lag(myTS2[,"Unemployment_Claims_Adj"], -10)),
  log(lag(myTS2[,"Unemployment_Claims_Adj"], -11)),
  log(lag(myTS2[,"Unemployment_Claims_Adj"], -22)),
  log(lag(myTS2[,"Unemployment_Claims_Adj"], -23)),
  lag(myTS2[,"GDP_YoY"], -1),
  lag(myTS2[,"GDP_YoY"], -3),
  lag(myTS2[,"GDP_YoY"], -19),
  lag(myTS2[,"PCE_YoY"], -18),
  lag(myTS2[,"PCE_YoY"], -19),
  lag(myTS2[,"PCE"], -20),
  myTS2[,"covidRec"],
  lag(myTS2[,"covidRec"], -2),
  lag(myTS2[,"greatRec"], -2),
  lag(myTS2[,"greatRec"], -6),
  lag(myTS2[,"greatRec"], -7),
  myTS2[,"early2000Rec"],
  lag(myTS2[,"Plans_to_Buy_Automobile"], -3),
  lag(myTS2[,"Plans_to_Buy_Automobile"], -10),
  lag(myTS2[,"Plans_to_Buy_Automobile"], -14),
  lag(myTS2[,"Plans_to_Buy_Automobile"], -19),
  lag(myTS2[,"Plans_to_Buy_Automobile"], -21),
  log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -3)),
  log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -7)),
  log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -10)),
  log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -11)),
  log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -12)),
  log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -13)),
  log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -15)),
  log(lag(myTS2[,"GDPYoYxUnempClaimsAdj"], -23)),
  lag(myTS2[,"CPIxDebt"], -20),
  lag(myTS2[,"CPIAdjxDebt"], -8),
  lag(myTS2[,"CPIAdjxDebt"], -10),
  lag(myTS2[,"CPIAdjxDebt"], -13),
  lag(myTS2[,"CPIAdjxDebt"], -14),
  lag(myTS2[,"CPIAdjxDebt"], -20))

# write.csv(allStepLags2, file = "Steplag2.csv")
```

```{r}
for(i in c(1:24, 30:37)){
  plot((log(myTS2[15:262,i])) ,leadFit$residuals,  main = colnames(myTS2)[i])
}
```

More likely to be Lagging:
Unemp Rate Adj, Unemp Claims, Hourly Earnings YoY, Debt, Home Sales Adj, Recessions

More likely to be leading:
S&P, GDP Unemp Rate, Hourly Earnings, CPI, Available Credit, Disp Income, Saving Rate, New Home Sales Adj

Lags:
Debt: -10, 11, 14
CPIADJ^2: 11

Leads:S&P +8, 10
GDP: 4, 10. Yoy 12
PCE: 5, 14, 18
Unemp Rate: 2, 5
Adj: 13
Unemp Claims: 1, 13,14
Hourly: 5. Adj 6
CPI: 6. Adj: 3, 15
Avail Cred: 12, 13, 17
Disp Income: 11 + 1to 24 YoY 11 + 16, 23
Savings: 4 + 11
Homes Adj: 1, 14 + 7, 15
New Homes Adj: 10,11,12 +13
GDPxUnemp: 1,2,13, 21 -2,13
UnempxSaving: 4 ,5
CPIADJ^2: 1,2,3
```{r}
wleads <- cbind(
  log(myTS2[,"XYZ_co_est_Monthly_Revenue"]),
  myTS2[,"novInd"],
  myTS2[,"decInd"],
  # myTS2[,"janInd"],
  # myTS2[,"febInd"],
  # myTS2[,"greatRec"],
  myTS2[,"covidRec"],

  # lag(myTS2[,"covidRec"],-3),
  # lag(myTS2[,"greatRec"], -7),
  # myTS2[,"janInd"],
  # lag(myTS2[,"S&P500"], 8),
  # lag(myTS2[,"S&P500"], 10),
  # lag(myTS2[,"GDP"], 4),
  # lag(myTS2[,"GDP"], 10),
  # lag(myTS2[,"PCE"], 5),
  # lag(myTS2[,"PCE"], 14),
  # lag(myTS2[,"PCE"], 18),
 # lag(myTS2[,"PCE_YoY"], -19),
 # log(lag(myTS2[,"Unemployment_Claims_Adj"], -11)) *lag(myTS2[,"covidRec"], -3),
 # log(myTS2[,"Unemployment_Claims_Adj"]) * lag(myTS2[,"covidRec"],-3),
  # lag(myTS2[,"Unemployment_Rate_Adj"], 13),
  # log(lag(myTS2[,"Unemployment_Claims_Adj"], -11)),
  log(lag(myTS2[,"Unemployment_Claims_Adj"], 2)),
  log(lag(myTS2[,"Unemployment_Claims_Adj"], 2))* lag(myTS2[,"covidRec"], -3),
  # log(lag(myTS2[,"Unemployment_Claims_Adj"], 13)),
  # log(lag(myTS2[,"Unemployment_Claims_Adj"], 14)),
  lag(myTS2[,"CPI_Adj"], -5)*myTS2[,"novInd"],
  # lag(myTS2[,"CPI_Adj"], 9)*myTS2[,"janInd"],
  # myTS2[,"decInd"] * myTS2[,"CPI_Adj"],
  lag(myTS2[,"CPI_Adj"], 3),
  # lag(myTS2[,"CPI_Adj"], 15),
  # lag(myTS2[,"CPI_Adj"], -19),
  # lag(myTS2[,"CPI_Adj_YoY"], -4) * lag(myTS2[,"greatRec"], -2),
  lag(myTS2[,"CPI_Adj"], 3)^2,
  # lag(myTS2[,"CPI_Adj"], 15),
  # lag(myTS2[,"Debt"], -10),
  # lag(myTS2[,"Debt"], -11),
  lag(myTS2[,"Debt"], -14),
  # lag(myTS2[,"Debt"], -14) *  lag(myTS2[,"covidRec"], -3),
  # lag(myTS2[,"Debt"], ),
  # lag(myTS2[,"Available_Credit"], 12),
  # lag(myTS2[,"Available_Credit"], 13),
  # log(lag(myTS2[,"Available_Credit"], 17)),
  # lag(myTS2[,"Available_Credit"], 17) * myTS2[,"covidRec"],
  # lag(myTS2[,"Disposable_Income"], 11),
  # lag(myTS2[,"Disposable_Income"], 16),
  # lag(myTS2[,"Disposable_Income"], 23),
  # lag(myTS2[,"Savings_Rate"], 4),
  # lag(myTS2[,"Savings_Rate"], 5),
  # lag(myTS2[,"Savings_Rate"], 5) *lag(myTS2[,"covidRec"], -3),
  # lag(myTS2[,"Savings_Rate"], 11),
  # lag(myTS2[,"Home_Sales_Adj"], 1),
  lag(myTS2[,"Home_Sales_Adj"], -17),
  # lag(myTS2[,"Home_Sales_Adj"], 7),
  # lag(myTS2[,"Home_Sales_Adj"], 14),
  # lag(myTS2[,"Home_Sales_Adj"], 15),
  lag(myTS2[,"New_Home_Sales_Adj"], -7)
  # lag(myTS2[,"New_Home_Sales_Adj"], 10),
  # lag(myTS2[,"New_Home_Sales_Adj"], 11)
  # lag(myTS2[,"New_Home_Sales_Adj"], 12),
  # lag(myTS2[,"New_Home_Sales_Adj"], 13)
  # lag(myTS2[,"UnempXSavings"], 4)
  # lag(myTS2[,"UnempXSavings"], 5)
  # lag(myTS2[,"S&P500"], -2),
  # lag(myTS2[,"GDP"], -20),
  # lag(myTS2[,"GDP_YoY"], -1),
  # lag(myTS2[,"PCE"], -20),
  # lag(myTS2[,"Unemployment_Rate"], -8),
  # lag(myTS2[,"Unemployment_Rate"], -20),
  # lag(myTS2[,"Unemployment_Rate_Adj"], -3),
  # lag(myTS2[,"Unemployment_Rate_Adj"], -11),
  # lag(myTS2[,"Unemployment_Rate_Adj"], -13),
  # myTS2[,"Unemployment_Claims"],
  # lag(myTS2[,"Unemployment_Claims"], -10),
  # lag(myTS2[,"CPI_Adj"], -12),
  # lag(myTS2[,"CPI_Adj"], -15),
  # lag(myTS2[,"Available_Credit"], -20),
  # lag(myTS2[,"CCI"], -2),
  # lag(myTS2[,"Debt"], -1),
  # lag(myTS2[,"Debt"], -6),
  # lag(myTS2[,"Debt"], -9),
  # lag(myTS2[,"Savings_Rate"], -8),
  # lag(myTS2[,"Savings_Rate"], -19),
  # lag(myTS2[,"Home_Sales_Adj"], -1),
  # lag(myTS2[,"Home_Sales_Adj"], -8),
  # lag(myTS2[,"Home_Sales_Adj"], -9),
  # lag(myTS2[,"Home_Sales_Adj"], -10),
  # myTS2[,"Plans_to_Buy_Automobile"]
  # lag(myTS2[,"isRecession"], -2)
)
#(2,0,0)(1,0,0)
leadFit <- Arima(log(wleads[15:262,1]), order = c(2,0,0), seasonal = list(order = c(1,0,0), period = 12),  xreg = wleads[15:262,-1])
# summary(leadFit)
pacf(leadFit$residuals, na.action = na.omit)
checkresiduals(leadFit)
coeftest(leadFit)

```

```{r}
exp(leadFit$coef)-1


```
```{r}


```



```{r}
wleadsAll <- cbind(
  myTS2[,"XYZ_co_est_Monthly_Revenue"],
  myTS2[,"novInd"],
  myTS2[,"decInd"],
  myTS2[,"greatRec"],
  myTS2[,"covidRec"],
  lag(myTS2[,"greatRec"], -7),
  myTS2[,"janInd"],
  lag(myTS2[,"S&P500"], 8),
  lag(myTS2[,"S&P500"], 10),
  lag(myTS2[,"GDP"], 4),
  lag(myTS2[,"GDP"], 10),
  lag(myTS2[,"PCE"], 5),
  lag(myTS2[,"PCE"], 14),
  lag(myTS2[,"PCE"], 18),
  lag(myTS2[,"Unemployment_Rate_Adj"], 13),
  log(lag(myTS2[,"Unemployment_Claims_Adj"], -11)),
  log(lag(myTS2[,"Unemployment_Claims_Adj"], 1)),
  log(lag(myTS2[,"Unemployment_Claims_Adj"], 13)),
  log(lag(myTS2[,"Unemployment_Claims_Adj"], 14)),
  lag(myTS2[,"CPI_Adj"], -5)*myTS2[,"novInd"],
  lag(myTS2[,"CPI_Adj"], 9)*myTS2[,"janInd"],
  myTS2[,"decInd"] * myTS2[,"CPI_Adj"],
  lag(myTS2[,"CPI_Adj"], 3),
  lag(myTS2[,"CPI_Adj"], -19),
  lag(myTS2[,"CPI_Adj"], 3)^2,
  lag(myTS2[,"CPI_Adj"], 15),
  lag(myTS2[,"Debt"], -10),
  lag(myTS2[,"Debt"], -11),
  lag(myTS2[,"Debt"], -14)^2,
  lag(myTS2[,"Available_Credit"], 12),
  lag(myTS2[,"Available_Credit"], 13),
  lag(myTS2[,"Available_Credit"], 17),
  lag(myTS2[,"Disposable_Income"], 11),
  lag(myTS2[,"Disposable_Income"], 16),
  lag(myTS2[,"Disposable_Income"], 23),
  lag(myTS2[,"Savings_Rate"], 4),
  lag(myTS2[,"Savings_Rate"], 11),
  lag(myTS2[,"Home_Sales_Adj"], 1),
  lag(myTS2[,"Home_Sales_Adj"], -17),
  lag(myTS2[,"Home_Sales_Adj"], 7),
  lag(myTS2[,"Home_Sales_Adj"], 14),
  lag(myTS2[,"Home_Sales_Adj"], 15),
  lag(myTS2[,"New_Home_Sales_Adj"], -7),
  lag(myTS2[,"New_Home_Sales_Adj"], 10),
  lag(myTS2[,"New_Home_Sales_Adj"], 11),
  lag(myTS2[,"New_Home_Sales_Adj"], 12),
  lag(myTS2[,"New_Home_Sales_Adj"], 13),
  lag(myTS2[,"UnempXSavings"], 4),
  lag(myTS2[,"UnempXSavings"], 5),
  lag(myTS2[,"CPIAdjSq"], 1),
  lag(myTS2[,"CPIAdjSq"], 2),
  lag(myTS2[,"CPIAdjSq"], 3),
  lag(myTS2[,"S&P500"], -2),
  lag(myTS2[,"GDP"], -20),
  lag(myTS2[,"GDP_YoY"], -1),
  lag(myTS2[,"PCE"], -20),
  lag(myTS2[,"Unemployment_Rate"], -8),
  lag(myTS2[,"Unemployment_Rate"], -20),
  lag(myTS2[,"Unemployment_Rate_Adj"], -3),
  lag(myTS2[,"Unemployment_Rate_Adj"], -11),
  lag(myTS2[,"Unemployment_Rate_Adj"], -13),
  myTS2[,"Unemployment_Claims"],
  lag(myTS2[,"Unemployment_Claims"], -10),
  lag(myTS2[,"CPI_Adj"], -12),
  lag(myTS2[,"CPI_Adj"], -15),
  lag(myTS2[,"Available_Credit"], -20),
  lag(myTS2[,"CCI"], -2),
  lag(myTS2[,"Debt"], -1),
  lag(myTS2[,"Debt"], -6),
  lag(myTS2[,"Debt"], -9),
  lag(myTS2[,"Savings_Rate"], -8),
  lag(myTS2[,"Savings_Rate"], -19),
  lag(myTS2[,"Home_Sales_Adj"], -1),
  lag(myTS2[,"Home_Sales_Adj"], -8),
  lag(myTS2[,"Home_Sales_Adj"], -9),
  lag(myTS2[,"Home_Sales_Adj"], -10),
  myTS2[,"Plans_to_Buy_Automobile"]
)
# write.csv(wleadsAll, file = "wleads.csv")


```
